### 2018-07-06 paper/3-abstractions.tex
Two minor rewordings
Drop TODOs and old comments

% TODO: Shall we describe the lifTask and liftTasks combinators? They aren't pretty.
%
%   liftTask :: Task Applicative k v -> Task Monad k v
%   liftTask (Task task) = Task task
%
%   liftTasks :: Tasks Applicative k v -> Tasks Monad k v
%   liftTasks = fmap (fmap liftTask)
%
% Notice also that, even though \hs{busy} takes a \hs{Task}~\hs{Monad} as its
% argument, an application of \hs{busy} to a \hs{Task}~\hs{Functor} or
% a \hs{Task}~\hs{Applicative} will typecheck and run just fine. It feels a bit like
% sub-typing, but is actually just ordinary higher-rank polymorphism at
% work~\cite{jones2007practical}.

@@

\begin{minted}[xleftmargin=5pt]{haskell}
compute :: Task Monad k v -> Store i k v -> v
compute task store = runIdentity $ run task (\k -> Identity (getValue k store))
\end{minted}

\noindent
Here we do not need any effects in the \hs{fetch} callback to \hs{task}, so
we can use the standard Haskell \hs{Identity} monad (Fig.~\ref{fig-stdlib}).
The use of \hs{Identity} just fixes the `impedance mismatch' between the
function \hs{getValue}, which returns a pure value~\hs{v}, and the \hs{fetch}
argument of the \hs{task}, which must return an \hs{f}~\hs{v} for some \hs{f}.
To fix the mismatch, we wrap the result of \hs{getValue} in the \hs{Identity}
monad: the function
\hs{\@@k}~\hs{->}~\hs{Identity}~\hs{(@@getValue}~\hs{k}~\hs{store)} has the type
\hs{k}~\hs{->}~\hs{Identity}~\hs{v}, and can now be passed to a \hs{task}. The
result comes as \hs{Identity}~\hs{v}, which we unwrap by \hs{runIdentity}.

% To fix the mismatch, we unwrap using the function \hs{runIdentity} of type \hs{Identity}~\hs{a}~\hs{->}~\hs{a},
% which both forces the monad to \hs{Identity} and strips it away.

@@

\begin{itemize}
    \item \hs{result} and \hs{store} \emph{agree on inputs}, that is, for all
    input keys \hs{k}~$\in$~$I$:
    \[
    \hs{getValue}~\hs{k}~\hs{result}~\hs{==}~\hs{getValue}~\hs{k}~\hs{store}.
    \]
    In other words, no inputs were corrupted during the
    build.
    %\footnote{\todo{SLPJ}{Add the joke that GHC used to delete inputs?}}.

>>>>

@@

\begin{minted}[xleftmargin=5pt]{haskell}
compute :: Task Monad k v -> Store i k v -> v
compute task store = runIdentity $ run task (\k -> Identity@\,@(getValue k store))
\end{minted}

\noindent
Here we do not need any effects in the \hs{fetch} callback to \hs{task}, so
we can use the standard Haskell \hs{Identity} monad (Fig.~\ref{fig-stdlib}).
The use of \hs{Identity} just fixes the `impedance mismatch' between the
function \hs{getValue}, which returns a pure value~\hs{v}, and the \hs{fetch}
argument of the \hs{task}, which must return an \hs{f}~\hs{v} for some \hs{f}.
To fix the mismatch, we wrap the result of \hs{getValue} in the \hs{Identity}
monad: the function
\hs{\@@k}~\hs{->}~\hs{Identity}~\hs{(@@getValue}~\hs{k}~\hs{store)} has the type
\hs{k}~\hs{->}~\hs{Identity}~\hs{v}, and can now be passed to a \hs{task}. The
result has type \hs{Identity}~\hs{v}, which we unwrap with \hs{runIdentity}.

% To fix the mismatch, we unwrap using the function \hs{runIdentity} of type
% \hs{Identity}~\hs{a}~\hs{->}~\hs{a},
% which both forces the monad to \hs{Identity} and strips it away.

@@

\begin{itemize}
    \item \hs{result} and \hs{store} \emph{agree on inputs}, that is, for all
    input keys \hs{k}~$\in$~$I$:
    \[
    \hs{getValue}~\hs{k}~\hs{result}~\hs{==}~\hs{getValue}~\hs{k}~\hs{store}.
    \]
    In other words, no inputs were corrupted during the
    build.
